Unsupervised embedding of trajectories captures the latent structure of mobility

### 2020-10-23 paper/current/main.tex
added word
tweaks to SK data

%
% Figure - SemAxis results
%
\begin{figure}[hp!]
	\centering
	\includegraphics[width=0.7\textwidth]{\figdir/SemAxis/semaxis_fig.pdf}
	\caption{
		\textbf{Embedding captures latent geography and prestige hierarchy.}
		\textbf{a.} Comparison between the ranking of organizations in the Times ranking and the embedding ranking derived using SemAxis.
		Un-filled points are those top and bottom five universities used span the axis.
	  	Even when considering only a total of ten organization vectors, the estimate of the Spearman's rank correlation between the embedding and Times ranking is $\rho = 0.73$ ($n = 145$), which increases when more top-and-bottom ranked universities are included (Fig.~\ref{fig:supp:semaxis_compare}).
	  	\textbf{b.} The Times ranking is correlated with Leiden Ranking of U.S. universities with Spearman's $\rho = 0.87$.
		\textbf{c-f.} Illustration of SemAxis projection along two axes;  \textit{latent geographic axis}, from California to Massachusetts (left to right) and the \textit{prestige axis}.
		Shown for U.S. Universities (\textbf{c}), regional and liberal arts colleges (\textbf{d}), Research institutes (\textbf{e}), and Government organizations (\textbf{f}).
		Full organization names listed in Table~\ref{table:supp:orglabels}.
	}
	\label{fig:semaxis}
\end{figure}

@@

\subsection*{Korean accommodation reservation data}
We source Korean accommodation reservation data from collaboration with Goodchoice Company LTD. in Korea, The data contain reservation trajectories of each customer spanning the time period of August 2018 through July 2020, and comprising 1,038 unique accommodation locations in Seoul, South Korea.

>>>>

%
% Figure - SemAxis results
%
\begin{figure}[hp!]
	\centering
	\includegraphics[width=0.7\textwidth]{\figdir/SemAxis/semaxis_fig.pdf}
	\caption{
		\textbf{Embedding captures latent geography and prestige hierarchy.}
		\textbf{a.} Comparison between the ranking of organizations in the Times ranking and the embedding ranking derived using SemAxis.
		Un-filled points are those top and bottom five universities used span the axis.
	  	Even when considering only a total of ten organization vectors, the estimate of the Spearman's rank correlation between the embedding and Times ranking is $\rho = 0.73$ ($n = 145$), which increases when more top-and-bottom ranked universities are included (Fig.~\ref{fig:supp:semaxis_compare}).
	  	\textbf{b.} The Times ranking is correlated with Leiden Ranking of U.S. universities with Spearman's $\rho = 0.87$.
		\textbf{c-f.} Illustration of SemAxis projection along two axes;  \textit{latent geographic axis}, from California to Massachusetts (left to right) and the \textit{prestige axis}.
		Shown for U.S. Universities (\textbf{c}), regional and liberal arts colleges (\textbf{d}), Research institutes (\textbf{e}), and Government organizations (\textbf{f}).
		Full organization names are listed in Table~\ref{table:supp:orglabels}.
	}
	\label{fig:semaxis}
\end{figure}

@@

\subsection*{Korean accommodation reservation data}
We source South Korean accommodation reservation data from collaboration with Goodchoice Company LTD. 
The data contains customer-level reservation trajectories spanning the time period of August 2018 through July 2020, and comprising 1,038 unique accommodation locations in Seoul, South Korea.
